When are Fuzzy Extractors Possible?

### 2014-10-03 info-bounds/FuzzyExtPossibility.tex
more polishing of the intro -- first two pages

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations, these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources it is often necessary to remove noise, in order to derive the same value in subsequent readings.

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms. The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.

The security requirement for fuzzy extractors that is $\key$ uniform even to an adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.

Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.  Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.  However, the lower bound is too imprecise (sometimes even negative) for practical settings.  As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}

\paragraph{Characterization  for Distribution-aware Extractability}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.

\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors". Also, "typically fuzzy extractors cannot be tailored". Also "for a family of sources" $\to$ "to a family of sources".}

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart. \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.

\paragraph{Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}). We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.  Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.

\begin{table}
\begin{center}
\begin{tabular}{c  l l }
 & Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}
\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}

\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch using precise knowledge of the distribution $W$.  We begin with distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  Consider some subsequent reading $w'$. At a minimum the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.   Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.  We use universal hashing to disambiguate points.

@@

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  The value $p$ partitions the metric space into regions that produce a consistent value in $\rep$.  For each of these regions the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it must put most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  In the \emph{distribution-aware} setting, the algorithms work for a single distribution $W$.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing} 
\vspace{.065in}
\end{minipage}  &
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
$W \leftarrow \mathcal{W}$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing}
\end{minipage}
\end{tabular}
\end{center}

%\begin{center}
%\begin{minipage}{1in}
%\end{center}

%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
%Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.

%\begin{center}
%\begin{minipage}{1in}
% \end{minipage} 
%\end{center}

The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.  In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.  These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{V}$ be a family of distributions.  If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.  Let $V$ be a distribution over elements of $\mathcal{V}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  We can think of the description of $W$ as side-information or leakage to the adversary.  The system designer, however never sees the particular outcome $W$.  This asymmetry will form the basis of our negative results.

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{V}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{V}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
\end{corollary}
%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

%In the standard definitions of fuzzy extractors and secure sketches the requirement is to work for all distributions from a particular family.  The reason for this is that the algorithm designer knows some properties of their input distribution but not the entire distribution.  We model this partial information by thinking of the distribution as coming from a family of distributions with those properties.  The requirement to work \emph{all} distributions allows the adversary to specify the distribution after seeing the algorithm.

%We show that any secure sketch that works for all well-spread distributions must write down a large number of bits~(matching our known constructions of secure sketches).

@@

\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.  
\end{theorem}

\begin{proof}
It will be convenient to think of a single distribution where the outcome $w$ is a two step process of first sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.  The adversary sees the information $W$, but the system designer does not.  We can think of the fuzzy extractor working for a distribution $V$ and the adversary receiving some side information $Z$~(which distribution was sampled).

We show that there exists distribution $V$ such that for any secure sketch $\Hav(V | \sketch(V), Z)$ is small.  We begin by describing our family $\mathcal{V}$.  $\mathcal{V}$ consists of the set of affine functions from one dimension to $\gamma$ dimensions.  % That is, we project a single point in the field to an arbitrary element in the metric space.
%In addition, the adversary learns the particular source that is being sketched while the system designer does not.  To simplify notation, we denote the source from the system designers point of view as $V$ and the adversary's additional information about the distribution as $Z$.  We will show a distribution $V$ that does not admit a secure sketch, and thus for any secure sketch construction is insecure for at least one element of the family.
Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over all such $W$.  Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. Fix some $4\le t < \gamma$.
We then show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious secure sketch for the elements of $V$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.  Our impossibility result says nothing about this weaker form of a secure sketch.  We do not that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

>>>>

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources, it is often necessary to remove noise, in order to derive the same value in subsequent readings.

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the noninteractive version of these problems, in which these tasks are performed together with a single message.

The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.   T
The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced precisely as long as the distance between $w$ and $w'$ is at most $t$.

The security requirement for fuzzy extractors that is $\key$ uniform even to a (computationally unbounded) adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.

Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 1-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

\paragraph{Stronger Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$), followed by randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in the first of these two steps dominate for typical sources and, indeed, this step is less well understood.\footnote{Randomness extractors have matching upper and lower bounds on the security loss: for every extra two bits of output key, they lose one bit of security} Formally, a secure sketch performs non-interactive information reconciliation via pair of algorithms: $\sketch$ takes $w$ and produces a nonsecret value $ss$, while $\rec$ takes a value $w'$ within distance $t$ of $w$ and uses $\sketch$ to output the original reading $w$.

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.  We begin with distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.   Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.  We use universal hashing to disambiguate points.

@@

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.  We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.  For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  We cover the distribution-aware setting in \secref{sec:distribution aware}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing} 
\vspace{.065in}
\end{minipage}  &
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, k)$: \\
$V \leftarrow \mathcal{A}(\mathcal{W})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
$W \leftarrow V$\\
If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing}
\end{minipage}
\end{tabular}
\end{center}

$V$ is a distribution over elements of $\mathcal{W}$.  The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.  In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{W}$ be a family of distributions.  If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.  Let $V$ be a distribution over $\mathcal{W}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

Our negative results will consider an adversary that specifies a distribution $V$ over $\mathcal{W}$.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  That is, $\sketch, \rec$ sees a distribution $V$ and the adversary seeing some side information $Z$ corresponding to the distribution $W$.

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
\end{corollary}

@@

\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.  
\end{theorem}

\begin{proof}
We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}$ be the set of all distributions of the form 
\[W =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} W_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  
This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over $\mathcal{W}$.  The adversary sees $V|Z$, that is, they see the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. 
Fix some $4\le t < \gamma$.
We then show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is distribution oblivious secure sketch for the elements of $\mathcal{W}$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.  Our impossibility result says nothing about this weaker form of a secure sketch.  We note that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
